2-factor-Hull-White\_model\_calibration

### 2020-04-09 Submission1.tex
Intro Revised

\section{Introduction
}
The pricing calculations in this paper concern a European up-and-out call option. The up-and-out option is a type barrier option that is worthless if the barrier price is reached or exceeded, but otherwise behaves exactly as a standard European call option. There are four main variants of barrier options, two of which are cancelled by reaching the barrier price (up-and-out and down-and-out) and two of which are only valid if the barrier is reached (up-and-in and down-and-in).

The standard European call option payoff formula can be applied with the addition of a check to determine if the barrier price was reached or exceeded, in which case the payoff is zero for the up-and-out option. The same approach could be applied with minor adjustments to price down-and-out, down-and-in or up-and-in barrier options.

@@

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{4}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{def} \PY{n+nf}{share\PYZus{}path}\PY{p}{(}\PY{n}{S\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{p}{,} \PY{n}{dT}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{S\PYZus{}0}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{cumsum}\PY{p}{(}\PY{p}{(}\PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{o}{\PYZhy{}}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{dT} \PY{o}{+} \PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}

\PY{k}{def} \PY{n+nf}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{10}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}\PY{p}{:}
    \PY{n}{corr\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{corr}\PY{p}{]}\PY{p}{,} \PY{p}{[}\PY{n}{corr}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{]}\PY{p}{)}
    \PY{n}{norm\PYZus{}matrix} \PY{o}{=} \PY{n}{stats}\PY{o}{.}\PY{n}{norm}\PY{o}{.}\PY{n}{rvs}\PY{p}{(}\PY{n}{size} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{timesteps}\PY{p}{]}\PY{p}{)}\PY{p}{)}
    \PY{n}{corr\PYZus{}norm\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{matmul}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{linalg}\PY{o}{.}\PY{n}{cholesky}\PY{p}{(}\PY{n}{corr\PYZus{}matrix}\PY{p}{)}\PY{p}{,} \PY{n}{norm\PYZus{}matrix}\PY{p}{)}

    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{0}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{share\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}

    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{firm\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}

    \PY{k}{return} \PY{p}{[}\PY{n}{share\PYZus{}price\PYZus{}path}\PY{p}{,}\PY{n}{firm\PYZus{}price\PYZus{}path}\PY{p}{]}  
\end{Verbatim}
\end{tcolorbox}

@@

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{5}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{}Testing share and firm price correlation}
\PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{20}
\PY{n}{test} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{20000}\PY{p}{)}

\PY{n}{share\PYZus{}ret} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{)}

\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{:}
    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
    \PY{n+nb}{print}\PY{p}{(}\PY{n}{stats}\PY{o}{.}\PY{n}{pearsonr}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

@@

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{11}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{} define payoff for up\PYZhy{}and\PYZhy{}out call option}
\PY{k}{def} \PY{n+nf}{payoff}\PY{p}{(}\PY{n}{S\PYZus{}t}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}\PY{p}{:}
    \PY{n}{stopped\PYZus{}S} \PY{o}{=} \PY{n}{S\PYZus{}t}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{where}\PY{p}{(}\PY{p}{(}\PY{n}{S\PYZus{}t} \PY{o}{\PYZlt{}} \PY{n}{L}\PY{p}{)}\PY{o}{.}\PY{n}{all}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}
    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{maximum}\PY{p}{(}\PY{n}{stopped\PYZus{}S} \PY{o}{\PYZhy{}} \PY{n}{K}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}

\PY{n}{payoff}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}12\PYZus{}months}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

@@

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{20}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}

\PY{k}{for} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{paths} \PY{o+ow}{in} \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{o}{.}\PY{n}{items}\PY{p}{(}\PY{p}{)}\PY{p}{:} 
    \PY{n}{payoffs} \PY{o}{=} \PY{n}{payoff}\PY{p}{(}\PY{n}{paths}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
    \PY{n}{option\PYZus{}price} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}

    \PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{=} \PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
    \PY{n}{amount\PYZus{}lost} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{recovery\PYZus{}rate}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{\PYZlt{}} \PY{n}{debt}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}

@@

% the second parameter MMMMM should be as long as the longest label you use, in my case Smoller -- if you use % numbers only, use 99
% use \cite{refname} to refer to bibliography item \bibitem{refname} 
% LaTeX assigns a number, unless you use \bibitem[Name]{refname} -- in this case
% LaTeX prints Name when you use \cite{refname}
\begin{thebibliography}{MMMMM} 
\bibitem{BA1} Blanchard, Arnaud. "The two-factor Hull-White model: pricing and calibration of interest rates derivatives." KTH Royal Institute of Technology (2014).

>>>>

\section{Introduction
}
A European up-and-out call option is type of a Barrier Option, these options are consider path-dependant because barrier option's payoff is based on the underlying stock's price path.  The payoff of an up-and-out option at maturity $T$ is given by,

\[
Payoff_T= (S_T - K)^+ given, max_{t \in [0,T]} S_t < L
\]
Where, where $K$ is the strike of the option, $L$ is the barrier level, and $S_t$ is the share price at time $t$.  This is a type of call option whose payoff is reduced to 0 if the share price crosses the barrier level. \\

The seminal work of Merton \cite{Merton1} pioneered the formula for pricing barrier options.  This led pricing formulas under the geometric Brownian motion (GBM) framework for one-asset barrier options by Rich \cite{RD1} and multi-asset barrier options by Wong and Kwok \cite{WK1}. Although the return dynamics of underlying shares are not sufficiently well described by the GBM process proposed by Black and Scholes \cite{BS1}, we are going to assume both the stock and counterparty firm values follow GBM  with constant drift and volatilities and default only occurs at maturity.

@@

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{4}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{k}{def} \PY{n+nf}{share\PYZus{}path}\PY{p}{(}\PY{n}{S\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{p}{,} \PY{n}{dT}\PY{p}{)}\PY{p}{:}
    \PY{k}{return} \PY{n}{S\PYZus{}0}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{cumsum}\PY{p}{(}\PY{p}{(}\PY{n}{risk\PYZus{}free\PYZus{}rate}\PY{o}{\PYZhy{}}\PY{n}{sigma}\PY{o}{*}\PY{o}{*}\PY{l+m+mi}{2}\PY{o}{/}\PY{l+m+mi}{2}\PY{p}{)}\PY{o}{*}\PY{n}{dT} \PY{o}{+} \PY{n}{sigma}\PY{o}{*}\PY{n}{np}\PY{o}{.}\PY{n}{sqrt}\PY{p}{(}\PY{n}{dT}\PY{p}{)}\PY{o}{*}\PY{n}{Z}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}
\PY{k}{def} \PY{n+nf}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{10}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{12}\PY{p}{)}\PY{p}{:}
    \PY{n}{corr\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{,} \PY{n}{corr}\PY{p}{]}\PY{p}{,} \PY{p}{[}\PY{n}{corr}\PY{p}{,} \PY{l+m+mi}{1}\PY{p}{]}\PY{p}{]}\PY{p}{)}
    \PY{n}{norm\PYZus{}matrix} \PY{o}{=} \PY{n}{stats}\PY{o}{.}\PY{n}{norm}\PY{o}{.}\PY{n}{rvs}\PY{p}{(}\PY{n}{size} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{array}\PY{p}{(}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{l+m+mi}{2}\PY{p}{,} \PY{n}{timesteps}\PY{p}{]}\PY{p}{)}\PY{p}{)}
    \PY{n}{corr\PYZus{}norm\PYZus{}matrix} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{matmul}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{linalg}\PY{o}{.}\PY{n}{cholesky}\PY{p}{(}\PY{n}{corr\PYZus{}matrix}\PY{p}{)}\PY{p}{,} \PY{n}{norm\PYZus{}matrix}\PY{p}{)}

    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{0}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
    \PY{n}{share\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{share\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{DataFrame}\PY{p}{(}\PY{n}{share\PYZus{}path}\PY{p}{(}\PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{Z}\PY{o}{=}\PY{n}{corr\PYZus{}norm\PYZus{}matrix}\PY{p}{[}\PY{p}{:}\PY{p}{,}\PY{l+m+mi}{1}\PY{p}{,}\PY{p}{]}\PY{p}{,} \PY{n}{dT}\PY{o}{=}\PY{l+m+mi}{1}\PY{o}{/}\PY{n}{timesteps}\PY{p}{)}\PY{p}{)}
    \PY{n}{firm\PYZus{}price\PYZus{}path} \PY{o}{=} \PY{n}{firm\PYZus{}price\PYZus{}path}\PY{o}{.}\PY{n}{transpose}\PY{p}{(}\PY{p}{)}
    \PY{k}{return} \PY{p}{[}\PY{n}{share\PYZus{}price\PYZus{}path}\PY{p}{,}\PY{n}{firm\PYZus{}price\PYZus{}path}\PY{p}{]}  
\end{Verbatim}
\end{tcolorbox}

@@

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{5}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{}Testing share and firm price correlation}
\PY{n}{sample\PYZus{}size} \PY{o}{=} \PY{l+m+mi}{20}
\PY{n}{test} \PY{o}{=} \PY{n}{generate\PYZus{}share\PYZus{}and\PYZus{}firm\PYZus{}price}\PY{p}{(}\PY{n}{S0}\PY{p}{,} \PY{n}{v\PYZus{}0}\PY{p}{,} \PY{n}{risk\PYZus{}free}\PY{p}{,} \PY{n}{sigma}\PY{p}{,} \PY{n}{sigma\PYZus{}firm}\PY{p}{,} \PY{n}{corr}\PY{p}{,} \PY{n}{T}\PY{p}{,} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{timesteps} \PY{o}{=} \PY{l+m+mi}{20000}\PY{p}{)}
\PY{n}{share\PYZus{}ret} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{)}
\PY{k}{for} \PY{n}{i} \PY{o+ow}{in} \PY{n+nb}{range}\PY{p}{(}\PY{n}{sample\PYZus{}size}\PY{p}{)}\PY{p}{:}
    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
    \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{log}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{n}{i}\PY{p}{]}\PY{p}{)}
    \PY{n+nb}{print}\PY{p}{(}\PY{n}{stats}\PY{o}{.}\PY{n}{pearsonr}\PY{p}{(}\PY{n}{test}\PY{p}{[}\PY{l+m+mi}{0}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{sharelog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{n}{test}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{firmlog}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{.}\PY{n}{diff}\PY{p}{(}\PY{p}{)}\PY{o}{.}\PY{n}{dropna}\PY{p}{(}\PY{p}{)}\PY{p}{)}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

@@

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{11}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{c+c1}{\PYZsh{} define payoff for up\PYZhy{}and\PYZhy{}out call option}
\PY{k}{def} \PY{n+nf}{payoff}\PY{p}{(}\PY{n}{S\PYZus{}t}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}\PY{p}{:}
    \PY{n}{stopped\PYZus{}S} \PY{o}{=} \PY{n}{S\PYZus{}t}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{where}\PY{p}{(}\PY{p}{(}\PY{n}{S\PYZus{}t} \PY{o}{\PYZlt{}} \PY{n}{L}\PY{p}{)}\PY{o}{.}\PY{n}{all}\PY{p}{(}\PY{p}{)}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}
    \PY{k}{return} \PY{n}{np}\PY{o}{.}\PY{n}{maximum}\PY{p}{(}\PY{n}{stopped\PYZus{}S} \PY{o}{\PYZhy{}} \PY{n}{K}\PY{p}{,} \PY{l+m+mi}{0}\PY{p}{)}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
\PY{n}{payoff}\PY{p}{(}\PY{n}{share\PYZus{}price\PYZus{}12\PYZus{}months}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
\end{Verbatim}
\end{tcolorbox}

@@

    \begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
\prompt{In}{incolor}{20}{\boxspacing}
\begin{Verbatim}[commandchars=\\\{\}]
\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}prices} \PY{o}{=} \PY{p}{[}\PY{p}{]}
\PY{n}{option\PYZus{}cva\PYZus{}adjusted\PYZus{}std} \PY{o}{=} \PY{p}{[}\PY{p}{]}
\PY{k}{for} \PY{n}{sample\PYZus{}size}\PY{p}{,} \PY{n}{paths} \PY{o+ow}{in} \PY{n}{share\PYZus{}price\PYZus{}paths}\PY{o}{.}\PY{n}{items}\PY{p}{(}\PY{p}{)}\PY{p}{:} 
    \PY{n}{payoffs} \PY{o}{=} \PY{n}{payoff}\PY{p}{(}\PY{n}{paths}\PY{p}{,} \PY{n}{K}\PY{p}{,} \PY{n}{L}\PY{p}{)}
    \PY{n}{option\PYZus{}price} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}
    \PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{=} \PY{n}{firm\PYZus{}val\PYZus{}paths}\PY{p}{[}\PY{n}{sample\PYZus{}size}\PY{p}{]}\PY{o}{.}\PY{n}{iloc}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{o}{.}\PY{n}{to\PYZus{}numpy}\PY{p}{(}\PY{p}{)}
    \PY{n}{amount\PYZus{}lost} \PY{o}{=} \PY{n}{np}\PY{o}{.}\PY{n}{exp}\PY{p}{(}\PY{o}{\PYZhy{}}\PY{n}{risk\PYZus{}free}\PY{o}{*}\PY{n}{T}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{l+m+mi}{1}\PY{o}{\PYZhy{}}\PY{n}{recovery\PYZus{}rate}\PY{p}{)}\PY{o}{*}\PY{p}{(}\PY{n}{term\PYZus{}firm\PYZus{}vals} \PY{o}{\PYZlt{}} \PY{n}{debt}\PY{p}{)}\PY{o}{*}\PY{n}{payoffs}

@@

% the second parameter MMMMM should be as long as the longest label you use, in my case Smoller -- if you use % numbers only, use 99
% use \cite{refname} to refer to bibliography item \bibitem{refname} 
% LaTeX assigns a number, unless you use \bibitem[Name]{refname} -- in this case
% LaTeX prints Name when you use \cite{refname}
\begin{thebibliography}{MMMMM} 
\bibitem{Merton1} Merton, Robert C. "Theory of rational option pricing." The Bell Journal of economics and management science (1973): 141-183.
\bibitem{RD1} Rich, Don R. "The mathematical foundations of barrier option-pricing theory." Advances in futures and options research 7 (1994).
\bibitem{WK1} Wong, Hoi Ying, and Yue‐Kuen Kwok. "Multi-asset barrier options and occupation time derivatives." Applied Mathematical Finance 10.3 (2003): 245-266.
\bibitem{BS1}Black, Fisher, and Myron Scholes. "The pricing and Corportate Liabilities." Journal of Political Economy 81 (1973).
\bibitem{You1} Yousuf, M. "A fourth-order smoothing scheme for pricing barrier options under stochastic volatility." International Journal of Computer Mathematics 86.6 (2009): 1054-1067.
